Deep Learning

### 2015-01-31 deepreview.tex
changed the redundancy explanation and fixed the Nair reference

Backpropagation provides an efficient way of computing gradients with respect to all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient. This
moves the weight vector in the direction of steepest descent in the
objective function. However, this is needlessly slow when the 
training set contains millions of cases and is highly redundant
with most examples conveying no new information about the mapping from
inputs to outputs.  It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient, times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients 
but these techniques are still the subject of controversy and are beyond
the scope of this review (see~\citet{Montavon2012} for tricks of the trade). 
However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

@@

The first major application of this pre-training approach was in speech
recognition and it was made possible by the advent of fast Graphics
Processing Units (GPUs) that were convenient to
program~\citep{RainaICML09-small}.  In 2009, the approach was used to map
short temporal windows of coefficients extracted from a soundwave to a set
of probabilities for the various fragments of speech that might be
represented by the frame in the center of the window.  It achieved
record-breaking results on a standard speech recognition benchmark that
used a small vocabulary~\citep{TIMITpaper} and was quickly developed to
give record-breaking results on a large vocabulary task~\citep{Dahl2012}.
By 2012, versions of the deep net from 2009 were being developed by many of
the major speech groups~\citep{Hinton-et-al-2012} and were already being
deployed in Android phones.  For smaller datasets, unsupervised
pre-training helps to prevent overfitting~\citep{Erhan+al-2010-small},
leading to significantly better generalization when the number of labeled
examples is small, or in a transfer setting where we have lots of
examples for some ``source'' tasks but very few for some ``target''
task. In this context, unsupervised representation learning helped to win
several transfer learning
competitions~\citep{UTLC+LISA-2011-small,Goodfellow-icml2012}.  Once deep
learning had been rehabilitated, it turned out that large labeled datasets
did not need the pre-training stage, provided the scales of the initial
random weights were carefully chosen to avoid very large or very small
initial gradients~\citep{GlorotAISTATS2010-small} and that even better
results (especially for very deep networks)
could be obtained by using rectifying non-linearities rather than
sigmoid or tanh
non-linearities~\citep{NairRelu,Glorot+al-AI-2011-small,Krizhevsky-2012-small,DahlRelu}.

>>>>

Backpropagation provides an efficient way of computing gradients with respect to all of
the weights in a layered network on a single training case, but there are
still many ways to make use of these gradients. The most obvious method is
to average the gradients over all of the cases in the training set and then
to change each weight in proportion to its negative gradient. This
moves the weight vector in the direction of steepest descent in the
objective function. 
%However, this is needlessly slow when the 
%training set contains millions of cases and is highly redundant
%with most examples conveying no new information about the mapping from
%inputs to outputs.  
However, this is needlessly slow when the 
training set contains millions of cases because each example or small batch of
examples can be seen as a noisy (but correct in average) version of the true total gradient: a very large
number of these noisy steps can converge much faster than very few but expensive clean steps because even
the clean gradient is not the optimal direction in which to go.
%
It is much faster to compute the average gradient
on a small ``mini-batch'' of randomly chosen training cases and to update
each weight by this stochastic estimate of its full gradient, times a
learning rate which decays as learning proceeds. Stochastic gradient
descent can be improved by using the history of the individual weight
gradients to adapt the learning rate for each weight~\citep{bottou-bousquet-2008-small}
or to provide additional increments that depend on earlier gradients 
but these techniques are still the subject of controversy and are beyond
the scope of this review (see~\citet{Montavon2012} for tricks of the trade). 
However, it is now widely accepted that some
form of stochastic gradient descent is the best bet for large, redundant
datasets.

@@

The first major application of this pre-training approach was in speech
recognition and it was made possible by the advent of fast Graphics
Processing Units (GPUs) that were convenient to
program~\citep{RainaICML09-small}.  In 2009, the approach was used to map
short temporal windows of coefficients extracted from a soundwave to a set
of probabilities for the various fragments of speech that might be
represented by the frame in the center of the window.  It achieved
record-breaking results on a standard speech recognition benchmark that
used a small vocabulary~\citep{TIMITpaper} and was quickly developed to
give record-breaking results on a large vocabulary task~\citep{Dahl2012}.
By 2012, versions of the deep net from 2009 were being developed by many of
the major speech groups~\citep{Hinton-et-al-2012} and were already being
deployed in Android phones.  For smaller datasets, unsupervised
pre-training helps to prevent overfitting~\citep{Erhan+al-2010-small},
leading to significantly better generalization when the number of labeled
examples is small, or in a transfer setting where we have lots of
examples for some ``source'' tasks but very few for some ``target''
task. In this context, unsupervised representation learning helped to win
several transfer learning
competitions~\citep{UTLC+LISA-2011-small,Goodfellow-icml2012}.  Once deep
learning had been rehabilitated, it turned out that large labeled datasets
did not need the pre-training stage, provided the scales of the initial
random weights were carefully chosen to avoid very large or very small
initial gradients~\citep{GlorotAISTATS2010-small} and that even better
results (especially for very deep networks)
could be obtained by using rectifying non-linearities rather than
sigmoid or tanh non-linearities
~\citep{Nair-2010-small,Glorot+al-AI-2011-small,Krizhevsky-2012-small,Dahl-et-al-ICASSP2013}.
